Congestion-Aware Join Optimization in Key-Value Stores

### 2014-08-01 paper/paper.tex
Add small note about RUBiS
Update paper abstract

\begin{abstract}
Applications which use key-value stores to execute higher-level queries may need to follow references obtained from previous keys.
In the case where all data is contained in main memory, the bottleneck becomes the network transfer of values from the datastore to the application.
When some keys become highly popular, network links to machines hosting these keys can become saturated and affect application performance.
We demonstrate an approach that takes advantage of replication and network performance measurements to effectively route requests over underutilized links.
\end{abstract}

@@

>>>>

\begin{abstract}
Applications which use key-value stores to execute higher-level queries need to aggregate data from multiple nodes.
In the case where all data is contained in main memory, the bottleneck becomes the network transfer of values from the datastore to the application.
When some keys become highly popular, network links to machines hosting these keys can become saturated and affect application performance.
In addition, nodes will compete with each other for bandwidth and uninformed traffic prioritization can result in reduced query execution time.
We demonstrate an approach that takes advantage of replication and network performance measurements to effectively route requests over underutilized links.
\end{abstract}

@@

Queries use data taken from the RUBiS~\cite{Cecchet2002} benchmark, which is a Web application simulating an online auction.
We distribute data on users and the items they are selling between all nodes with no replication.
